\chapter{First measurement method}

\section{Bad pattern}
\label{badtests}

We first used a two pad pattern, which is not very practical to make 4 probe measurements, since I either had to put two needles of the probestation on one pad or bound samples stage pad to one another. We finished the samples that were already written with EBL and the we switched to 4 pads patterns.


\section{Bad way of measuring}
\label{badmeasures}
At the beginning, with the 2 pads samples and with the first 4 pads samples, I bounded the samples to a sample stage to measure them with a complicated Matlab assisted setup.
\chapter{Failed Samples}
\section{Failure due to plasma}
\label{badplasma}
The plasma sometimes had some troubles and did not work properly. In the report there were the good samples but the plasma often burned the resist so that the copper evaporation could not be done properly.

\section{Failure due to EBL}
The first EBL writting we made with the 4 pad pattern failed, there was a height problem. The wafer was not complete so it could not be clamped properly with the regular clamps, we had to had another one, which we forgot. The writting was really not usable as we saw with the first evaporation. Of course, we made another one to check that the problem really came from the EBL writting and not from the LISA.
\chapter{Parameters table of the samples}
\label{parametertable}

\begin{tabular}{|c|c|c|c|c|c|}

        \hline
        \textsc{Test n\textdegree}&\textsc{Strong}&\textsc{Plasma}&\textsc{Regular}&\textsc{Comment}\\
        &\textsc{Oxidation}&&\textsc{Oxidation}&\\
        \hline
        Test 10&  &&&Failed EBL\\
        \hline
        Test 11&  &&&Failed EBL\\
        \hline
        Test 12&No&No&No&Clean contact reference\\
        \hline
        Test 13.i&Yes&10 min&No&Several positions\\
        \hline
        Test 14.i&Yes&20 min&No&Several positions\\
        \hline
        Test 15&Yes&No&No&Strong Oxidation reference\\
        \hline
        Test 16&No&No&Yes&Reference Sample Test 17\\
        \hline
        Test 17&Yes&10 min&Yes&Resist burned\\
        \hline
        Test 18&Yes&10 min&Yes&Resist burned\\
        \hline
        Test 19&No&No&Yes&Reference Sample Test 18\\
        \hline
        Test 20&Yes&10 min&Yes&Resist burned\\
        \hline
        Test 21&No&No&Yes&Reference Sample Test 20\\
        \hline
        Test 22&Yes&5 min&No&\\
        \hline
        Test 23&Yes&2 min 30s&No&\\
        \hline
        Test 24&Yes&10 min&Yes&Etched the wafer\\
        \hline
        Test 25&No&No&Yes&Reference Sample Test 24\\
        \hline
        Test 26&Yes&2 min&Yes&\\
        \hline
        Test 27&No&No&Yes&Reference sample Test 26\\
        \hline
        \end{tabular}
\vspace{0.5cm}

\noindent Parameters : 
\begin{itemize}
    \item Strong Oxidation = 10 min under a pressure of 200 mbar of O$_2$
    \item Regular Oxidation = 2 min under a pressure of 2 mbar of O$_2$
    \item Plasma = Pressure of Ar of 4.10$^{-4}$ mbar, Power=40mA, Extraction=-0.8kV\footnote{Lowered to -0.25kV starting from Test 22}, Ion Energy=1.5kV 
\end{itemize}

\chapter{Compléments de résultats}

\section{Images SEM}

\section{Graphes supplémentaires}
